---
title: "Explore species traits coordination"
author: "Anne-Cecile Colin"
date: "11/06/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(devtools)
library(readr)
library(sp)
library(raster)
library(stats)
library(plyr)
library(dplyr)
library(readxl)
library(ggplot2)

setwd("C:/ACFolder/Research projects/phyloGWAS CurrencyCreek/R projects/EucsDroughtTraitsCoordination")
```


## Exploring the data and asking questions...

d13C is a predictor of drought tolerance in Eucalyptus species, same for other traits related to water transport/storage efficiency such as WD, SLA, totalC and N; and life-history traits conserved related to the species biological niche such as maximum height,


 * Is the d13C correlated with the impact of drought on species at the CCA?
To answer that question we can use a GLMM an control for the year (block design).
Null hypothesis: d13C is not correlated with species' x variable (drought variable in climate of origin)
Statistical test: GLMM d13C ~ +(1|year)

```{r testing for }

```

## Plotting species trait data

Then we can plot traits against each other to explore the data a little bit:
``` {r d13C against MAP}

plot.map.d13c <- ggplot(data = u_full.df, mapping = aes(x = MAP, y = d13C)) + 
  geom_point(mapping = aes(color = Section))+
  facet_grid(Section ~ .)

print(plot.map.d13c)
dev.print(pdf, 'plots/plot_d13C_MAP_sections.pdf')
```


``` {r d13C against latitude of tree's homesite}
plot.map.latitude <- ggplot(data = u_full.df, mapping = aes(x = latitude, y = d13C)) + 
  geom_point(mapping = aes(color = Section)) +
  facet_grid(Section ~ .)

print(plot.map.latitude)
dev.print(pdf, 'plots/plot_d13C_latitude_sections.pdf')

```

``` {r d13C against AI}
plot.map.AI <- ggplot(data = full.df, mapping = aes(x = AICorrected.y, y = d13C)) + 
  geom_point(mapping = aes(color = Section.x))+
  facet_grid(Section.x ~ .)

print(plot.map.AI)
dev.print(pdf, 'plots/plot_d13C_aridityindex_sections.pdf')
```

``` {r d13C against maximum height}
plot.d13C.MH <- ggplot(data = cca_filtered, mapping = aes(x = maximumheight, y = d13C)) + 
  geom_point(mapping = aes(color = Section))+
  facet_grid(Section ~ .)

print(plot.map.AI)
dev.print(pdf, 'plots/plot_d13C_aridityindex_sections.pdf')
```

## Visualize traits and environmental coordination with pairwise interaction:

```{r pairwise environemtnal variables interactions}
eucstraits <-read.csv("../data/species_dataset.csv")
view(eucstraits)
Section <- factor(eucstraits$Section)
pairs(eucstraits[,c(24:44)], col = Section, upper.panel = NULL, pch = 16, cex = 0.5) # [-1] takes all variables

with(eucstraits, plot(TWQ, PDM, cex=1, pch=16, col= "violetred3"))
str(eucstraits)
plot.TWQ.PDM <- ggplot(data = eucstraits, mapping = aes(x = TWQ, y = PDM)) + 
  geom_point(mapping = aes(color = Section)) #+
  facet_grid(Section ~ .)

print(plot.TWQ.PDM)

plot.WD.MAP <- ggplot(data = eucstraits, mapping = aes(x = MAT, y = MAP)) + 
  geom_point(mapping = aes(color = Section)) #+
  facet_grid(Section ~ .)
print(plot.WD.MAP)
```
## PCA analysis of functional and life-history traits related to drought

Functional and life-history traits related to drought are coordinated in drought response in different trade-offs and vary according to the climates of origin.
Here we explore what explains the variance and how much.

```{r PCA analysis}
#Doing the PCA
eucstraits <- read.csv2()

eucstraits.pca <- prcomp(eucstraits[,c(1:7)],center = TRUE, scale. = TRUE) ## taking all rows of column 1 to 7

summary(eucstraits.pca)

str(eucstraits.pca)
# Plotting the PCA
library(devtools)
install_github("vqv/ggbiplot")

library(ggbiplot)
ggbiplot(eucstraits.pca,
         ellipse = FALSE,#look at other PCs (here PC1 and PC2 specified in choices) 
         choices = c(1,2),
         circle = FALSE, # put circle around center to see variability of samples
         obs.scale = 1, #scaling samples
         var.scale = 1, #scaling variables
         labels = species(eucstraits), #sample lables
         var.axes= TRUE, # showing variables arrows on plot
         groups = series) + # series for grouping samples
  scale_colour_manual(name="Origin", values= c("forest green", "red3", "dark blue")) +
  ggtitle("PCA of ...") +
  theme_minimal()+
  theme(legend.position = "bottom")


# Adding other samples in
additionalsample <- c(#string of data listed according to variables in dataset for this sample)

eucstraitsplus <- rbind(eucstraits, additionalsample)

eucstraitsplus.pca <- prcomp(eucstraitsplus[,c(1:7)], center = TRUE, scale. = TRUE)
# then plot like above but using eucstraitsplus.pca for dataset 
```