---
title: "Creating a map of the geographical distribution of the Eucalyptus phyloGWAS dataset (Adna and Exs)"
author: "Anne-Cecile Colin"
date: "15/06/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library('tidyverse')
library('ggrepel')
library('leaflet')
library('sf')
library('raster')
library('rgdal')
library('ggmap')
sites <- read.csv("../data/AC_species_functional_traits_latlongs_climate.csv")
```

```{r dataset, echo=FALSE}
summary(sites)
str(sites)
view(sites)
```

```{r Aus map}
m1 <- get_stamenmap( bbox = c(left = 110, bottom = -45, right = 160, top = -10),
zoom = 4, maptype = "toner-background")
m1map <- ggmap(m1) +
  geom_point(data = sites, aes(x=longitude,y=latitude,col=Section)) +
  labs(title= "Coordinate data of species sampling points across Australia", 
                x="Longitude", y= "Latitude")


pdf("../plots/sp_sampling_sites.pdf")
plot(m1map)
dev.off()
```

## Plotting species sampling points onto Australia's climate zones from the Aus' Bureau of Meteorology:

First, reading data and converting as a raster:
``` {r straya climate zones raster}
infile <- "../data/kpn/kpnall.txt"
data <- as.matrix(read.table(infile, skip = 6)) 
data[data == -9999] = NA
rr <- raster(data, crs = "+init=epsg:4326")
extent(rr) = c(112, 112+0.025*1681, -44, -44+0.025*1361)

rr
```

``` {r converting raster values as tibble}
adm <- getData("GADM", country="AUS", level=1)
rr = mask(rr, adm)

gplot_data <- function(x, maxpixels = 50000)  {
  x <- raster::sampleRegular(x, maxpixels, asRaster = TRUE)
  coords <- raster::xyFromCell(x, seq_len(raster::ncell(x)))
  ## Extract values
  dat <- utils::stack(as.data.frame(raster::getValues(x))) 
  names(dat) <- c('value', 'variable')

  dat <- dplyr::as.tbl(data.frame(coords, dat))

  if (!is.null(levels(x))) {
    dat <- dplyr::left_join(dat, levels(x)[[1]], 
                            by = c("value" = "ID"))
  }
  dat
}
gplot_data(rr)
```
Then plotting the data:
``` {r plotting climate zones}
adm <- getData("GADM", country="AUS", level=1)
rr = mask(rr, adm)
rr <- as.data.frame(rr)
fortify(rr)
ggplot(rr) +
  labs(title= "Australia's climate zones",
       x="Longitude", y= "Latitude")
## come back to this stage and learn how to plot raster and points together with ggplot2 (look at thread in last tab)
gg

test_rr <- as(rr, "SpatialPixelsDataFrame")
test_rr <- as.data.frame(test_rr)
colnames(test_rr) <- c("layer", "x", "y")
str(test_rr)
```

``` {r plotting sampling points}
library(raster)
library(rgeos)
library(ggplot2)
library(ggthemes)

straya <- gSimplify(getData("GADM", country= "AUS", level=1), tol=0.001, TRUE)
straya <- fortify(straya)

st <- read.csv("../data/species_coordinates.csv")
st$color <- "violetred3"
st[st$section %in% c('Exsertaria'),]$color <- "skyblue4" 
view(st)
summary(st)

testplot <- ggplot() +
  geom_tile(data=test_rr, aes(x, y, layer))

testplot
gg <- ggplot() +
  #geom_map(data=straya, map=straya, map_id = 1) + 
  geom_tile(data=test_rr, aes(x=x, y=y, fill=layer)) +
                    #aes(x=long, y=lat, map_id=id, group=group),
                    #fill=NA, color="black") +
  #geom_point(data=st, aes(x=longitude, y=latitude, color = color), 
                      #alpha=1, na.rm=TRUE) +
  scale_size(range=c(2,7)) +
  scale_color_identity() +
  labs(title= "Coordinate data of species sampling points across Australia's climate zones", 
                x="Longitude", y= "Latitude") +
  coord_map() +
  theme_map() +
  theme(title= element_text(hjust = 0.5, vjust=1, face="bold"))
gg

```

``` {r zoom on specific site}
xmin <- # long minus
xmax <- # long plus
ymin <- # lat minus
ymax <- # lat plus

m2 <- get_stamenmap(bbox = c(left = xmin,
                             bottom = ymin,
                             right = xmax,
                             top = ymax),
                    zoom = 8, maptype = "terrain")
ggmap(m2) +
  geom_point(data = sites,
             aes(x=longitude,y=latitude,col=series))
```

``` {r cleaner way to select sites}
xmin2 <- 149.07
xmax2 <- 149.18
ymin2 <- -35.31
ymax2 <- -35.25

sitesClose <- sites %>% dplyr::filter(longitude > xmin2,
                                      longitude < xmax2,
                                      latitude > ymin2,
                                      latitude < ymax2)
library(ggrepel)

ggmap(m4) +
  geom_point(data = sitesClose, aes(x=longitude,y=latitude,col=depth)) +
  geom_label_repel(data = sitesClose,
                   aes(x=longitude,
                       y=latitude,
                       col=depth,
                       label=species_name),
                   box.padding = 0.9)
```

## Climate envelope of selected species:

BIOCLIM are the Worldclim bioclimatic variables.
 BIOCLIM Variables:
*BIO1 = Annual Mean Temperature*
BIO2 = Mean Diurnal Range (Mean of monthly (max temp - min temp))
BIO3 = Isothermality (BIO2/BIO7) (* 100)
BIO4 = Temperature Seasonality (standard deviation *100)
*BIO5 = Max Temperature of Warmest Month*
BIO6 = Min Temperature of Coldest Month
BIO7 = Temperature Annual Range (BIO5-BIO6)
BIO8 = Mean Temperature of Wettest Quarter
BIO9 = Mean Temperature of Driest Quarter
BIO10 = Mean Temperature of Warmest Quarter
BIO11 = Mean Temperature of Coldest Quarter
*BIO12 = Annual Precipitation*
BIO13 = Precipitation of Wettest Month
*BIO14 = Precipitation of Driest Month*
BIO15 = Precipitation Seasonality (Coefficient of Variation)
BIO16 = Precipitation of Wettest Quarter
BIO17 = Precipitation of Driest Quarter
BIO18 = Precipitation of Warmest Quarter
BIO19 = Precipitation of Coldest Quarter

``` {r showing climate enveloppe}
library(raster)
library(sp)
library(knitr)

r <- getData("worldclim",var="bio",res=2.5)
?getData
r <- r[[c(1:19)]]
names(r) <- c("BIO1","BIO2","BIO3","BIO4","BIO5","BIO6",
              "BIO7","BIO8","BIO9","BIO10","BIO11","BIO12",
              "BIO13","BIO14","BIO15","BIO16","BIO17","BIO18","BIO19")
#extract raster points
values <- raster::extract(r, st)

#project the samples
points <- SpatialPoints(unique(st), proj4string = r@crs)
plot(points)
head(points)

```

```{r Plotting trees sample location by climate vaiables}

with(final.df, plot(BIO5, BIO14, cex=1, pch=16, col="grey46"))
with(final.df, plot(BIO1, BIO12, cex=1, pch=16, col="grey46"))
```
